Notes and other text

### 2023-04-14 doc/manuscript/translocation.qmd
Added comments and text from Allie to Discussion

<!--# Bree comment: It seems to me that this paragraph might be better as a shorter high level compelling summary and then the subsequent sections of the Discussion go into each of the four lines of evidence in more detail. Otherwise it feels a bit heavy and I'm not sure readers will be able to hold it all in mind at once. Mark here: I have broken this paragraph up in to two and tried to keep descriptions pretty short.  -->

@@

@@

-   <!--# Allie text -->

    One thing we could think about discussing is that we really don't know the effect of some of the genomic changes we describe (i.e., do the changes increase or decrease overall expression of that gene in response to Bd).
    For MYLF evidence suggests that they probably need a bit MORE of an immune response because of findings showing very little response in susceptible animals (Rosenblum et al. 2012) however many studies have found that immune overactivation is linked to susceptibility for Bd.
    This could be different for populations with different histories of Bd exposure.
    Perhaps Rana muscosa has a more recent history with Bd (maybe with another lineage) than for instance Atelopus.
    All of this has led to me think this whole question deserves another paper integrating the Atelopus and MYLF datasets, so maybe we save all this for that?
    Open to whatever you all think is relevant to this story.

@@

<!--# Previous text from Allie below -->

<!--# The next 2 paragraphs are new text from Allie -->

>>>>

@@

<!--# Comment from Allie that will be helpful in making the cases that what we are seeing is evidence of strong selection/evolutionary rescue -->

For the question about describing what we are seeing as evolutionary rescue - I feel comfortable and confident using that wording for two reasons:

1\) STRENGTH OF SIGNAL: the gene regions we discuss specifically in our dataset are robust outliers.
In the case of the MHC region we have multiple SNPs in this region that are statistically significantly associated AND a larger pattern of depressed pi in the recovering pops and large Fst.
In the case of GVINP1 we have the only instance of two adjacent outlier spline windows for pi, and the largest difference in pi of any region we measured.
Finally for RIN3 the allele frequency maps tell the most compelling story and reflect the fact that this is the most statistically significantly outlier SNP that has an annotation.
and

2\) CORROBORATING STUDIES. For each gene mentioned above we can list many studies that have linked the genes to Bd/disease/wounds.
In the case of GVINP1 for instance there are at least three Bd transcriptomic studies that have found this specific gene to be differentially expressed in amphibians (I currently only cite one in the paper but could add the other two: Grogan et al. 2018, Ellison et al. 2014a, Ellison et al. 2014b).
In fact, if you haven't taken a look at the Grogan paper it is really interesting because it is similar in that they are describing evolution in natural settings and they talk a lot about the GVINP1 gene.
Even more remarkable that this gene was also linked so strongly to gill amoebic disease in salmon (explaining an astounding 20% of the resistance phenotype).

<!--# End of comment -->

@@

-   One thing we could think about discussing is that we really don't know the effect of some of the genomic changes we describe (i.e., do the changes increase or decrease overall expression of that gene in response to Bd).
    For MYLF evidence suggests that they probably need a bit MORE of an immune response because of findings showing very little response in susceptible animals (Rosenblum et al. 2012) however many studies have found that immune overactivation is linked to susceptibility for Bd.
    This could be different for populations with different histories of Bd exposure.
    Perhaps Rana muscosa has a more recent history with Bd (maybe with another lineage) than for instance Atelopus.
    All of this has led to me think this whole question deserves another paper integrating the Atelopus and MYLF datasets, so maybe we save all this for that?
    Open to whatever you all think is relevant to this story.

@@
